Scheduling and Vectorization for MPC

### 2022-03-16 paper_SIMD.tex
Minor change in Extension with arrays.

Our compiler performs the following semantic analysis steps:

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}: TODO
  \item
        \textbf{SSA conversion}:
        Convert the 3-address CFG to SSA with Cytron's algorithm.
\end{enumerate}

@@

\item inner-to-outer $X \rightarrow Y$. If dimensionality of the loop enclosure of $X$ is greater than the canonical dimensionality of the array, then add \emph{drop\_dim(...)} at $Y$, as in Basic Vectorization. Otherwise, do nothing.

>>>>

@@

\item inner-to-outer $X \rightarrow Y$. If dimensionality of the loop enclosure of $X$ is greater than the canonical dimensionality of the array, then add \emph{drop\_dim(...)} at $Y$, as in Basic Vectorization. Otherwise, do nothing. \ana{I think it will be better to add drop dim and raise dim as in the previous case but change the semantics of both as written here.}
